% Keywords: Bootstrap, Chakra UI, Node.js, Express.js, Git, Docker, Anaconda, Google Cloud Platform, VS Code, Visual Studio, Eclipse, JQuery, Postman %

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-10pt}\bfseries\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
    \item\small{
    {#1 \vspace{-5pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeItemBold}[2]{\resumeItem{\textbf{#1}: #2}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{\makebox[1.001\textwidth][r]{Feras Aljoudi-\thepage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Feras Aljoudi}
    \\ \vspace{1pt}
    \href{https://aljoudi.ca}{\underline{Portfolio}} $|$ 
    \href{https://resume.aljoudi.ca}{\underline{Virtual Resume}}
    \\ \vspace{1pt}
    \small Email: \href{mailto:feras.aljoudi@gmail.com}{\underline{feras.aljoudi@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/feras-aljoudi-79830b2a2/}{\underline{LinkedIn}} $|$ \href{https://github.com/ferasaljoudi}{\underline{GitHub}}
    \\ \vspace{2pt}
    \small Address: Regina, SK, Canada
    \\ \vspace{-4pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Co-op, Bioinformatic Programmer}{Sep. 2022 - Apr. 2023}
            {Agriculture\&Agri Food Canada}{Remote}
        \resumeItemListStart
            \resumeItem{Comprehensive documentation of software tools and workflows.}
            \resumeItem{Generating dot plots using Gnuplot software and Mummer software in Linux.}
            \resumeItem{Genetic variant identification using C++, Java, and Python languages.}
            \resumeItem{Advanced Data Analysis through Sequence Comparison.}
            \resumeItem{Impact on public health through Bioinformatics.}
        \resumeItemListEnd

        \resumeSubheading
            {Co-op, Electrical Engineering Intern}{Jan. 2022 - Aug. 2022}
            {SaskPower}{Regina, SK}
        \resumeItemListStart
            \resumeItem{Preparing contract’s documents between SaskPower and the contractors.}
            \resumeItem{Contacting vendors and purchasing the required equipment through emails.}
            \resumeItem{Preparing Excel sheets and PowerPoint presentations in Microsoft 365.}
            \resumeItem{Identifying the scope of work with the contractor while visiting the field.}
            \resumeItem{Uninstalling relays and switches and salvaging them in the proper containers.}
        \resumeItemListEnd

        \resumeSubheading
            {Store Manager}{Nov. 2018 - Dec. 2022}
            {YM Inc Urban Planet}{Regina, SK}
        \resumeItemListStart
            \resumeItem{Managing schedules and making sure the store needs are covered.}
            \resumeItem{Making monthly sales targets.}
            \resumeItem{Analyzing the business based on the top sellers in the store and the company.}
            \resumeItem{Assisting customers and making sure they were satisfied.}
            \resumeItem{Managing the wage cost and performing partnership with other banners.}
        \resumeItemListEnd

        \resumeSubheading
            {Project Coordinator}{Jan. 2018 - May 2018}
            {ZGEMI}{Regina, SK}
        \resumeItemListStart
            \resumeItem{Supervising the laborers and making sure the tasks were getting completed.}
            \resumeItem{Measuring the area of the rooms and walls.}
            \resumeItem{Completing the final report for each room and reporting any uncompleted work.}
            \resumeItem{Recording and adding hours and wage through the Microsoft Office – Excel.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Skills}
        \resumeItemListStart
            \resumeItemBold{Programming}{C++, C, C\#, Python, Java, HTML, CSS, React, Vue, JavaScript, PHP, TypeScript, ShellScript, ARM and MIPS Assembly, SQL, MySQL, Firebase, VHDL}
            \resumeItemBold{Web development}{WordPress, Figma}
            \resumeItemBold{Machine learning}{TensorFlow, Keras, NumPy, Pandas, Matplotlib, OpenCV}
            \resumeItemBold{Modeling programs}{Implement the best solution based on the needs by Solid Edge}
            \resumeItemBold{Other skills}{Management experience, computer experience, technical documentation, business analysis, vendor communication, team supervision, product management}
        \resumeItemListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Projects}
    \resumeSubHeadingListStart
        \resumeSubheading
            {IFS DriverAlert, Machine Learning}{Apr. 2025}
            {Graduation Project}{}
            \resumeItemListStart
                \resumeItem{Developed a real-time driver drowsiness detection system using Python, OpenCV, MediaPipe, and a trained CNN model with TensorFlow/Keras.}
                \resumeItem{Optimized the system for deployment on Raspberry Pi 5, ensuring efficient performance and low latency.}
                \resumeItem{Integrated hardware components including GPIO-connected switches, USB stereo speakers, and camera for seamless system functionality.}
                \resumeItem{Designed a privacy-focused offline solution, processing data in real-time without storing or transmitting user information.}
                \resumeItem{Built the system using open-source tools and libraries, showcasing expertise in hardware-software integration, embedded systems, and real-time image processing.}
                \resumeItem{To view full details: \href{https://github.com/ferasaljoudi/Capstone}{\underline{Capstone}}}
            \resumeItemListEnd

        \resumeSubheading
            {FIA-Local Service Finder}{Jul. 2024}
            {ENSE375 class}{}
            \resumeItemListStart
                \resumeItem{Collaborated with a team to develop a secure service platform using Java (Spring Boot) for backend and React.js for frontend, enabling users to list, search, and manage services.}
                \resumeItem{Implemented user authentication and data management to ensure secure login, registration, and profile updates.}
                \resumeItem{Designed and integrated responsive user interfaces for seamless service discovery, focusing on usability and accessibility.}
                \resumeItem{Conducted comprehensive testing, including boundary value analysis and integration testing, to ensure system reliability and robust performance.}
                \resumeItem{To view full details: \href{https://github.com/ferasaljoudi/FIA-Local-Service-Finder}{\underline{FIA-LocalServiceFinder}}}
            \resumeItemListEnd

        \resumeSubheading
            {Top Languages Service}{Jun. 2024}
            {Personal}{}
            \resumeItemListStart
                \resumeItem{Developed a web service providing API endpoints to generate visual language usage insights for GitHub users.}
                \resumeItem{Enabled customization options, including format, title color, and background color, for personalized output.}
                \resumeItem{Designed the service for public use, supporting data from both forked and original repositories for comprehensive analysis.}
                \resumeItem{To view full details: \href{https://github.com/ferasaljoudi/TopLanguages}{\underline{TopLanguages}}}
            \resumeItemListEnd
            
        \resumeSubheading
            {STM32-Based Smart Parking Management System}{Mar. 2024}
            {ENEL351 class}{}
            \resumeItemListStart
                \resumeItem{Engineered a smart parking solution using STM32 microcontroller, featuring real-time parking availability display, automated gate operation, and fire alarm.}
                \resumeItem{Incorporated servo motors and various sensors including pressure, infrared (IR), and gas sensors to manage parking operations.}
                \resumeItem{Programmed the entire system in embedded C with a modular design approach for easy maintenance and scalability.}
                \resumeItem{To view full details: \href{https://github.com/ferasaljoudi/AljoudiParkingSystem}{\underline{AljoudiParkingSystem}}}
            \resumeItemListEnd

        \resumeSubheading
            {Embedded Systems and Interactive Game Design}{Nov. 2023}
            {ENSE352 class}{}
            \resumeItemListStart
                \resumeItem{Engineered a Simon Game using C with an STM32 Nucleo Board for hardware interfacing, featuring 10 levels of increasing difficulty, input handling, and visual feedback.}
                \resumeItem{Utilized classic "Cylon Eye Scanner" start sequence and level progress/failure indicators.}
                \resumeItem{Applied time constraints to user inputs for enhanced gameplay challenge and utilized an isolated resistor for LED current regulation.}
                \resumeItem{To view full details: \href{https://github.com/ferasaljoudi/SimonGame}{\underline{SimonGame}}}
            \resumeItemListEnd

        \resumeSubheading
            {FPGA-Based Digital Scheduling and Display System}{Nov. 2023}
            {ENEL384 class}{}
            \resumeItemListStart
                \resumeItem{Developed a class scheduling digital circuit on a BASYS-3 FPGA board using VHDL in Vivado, featuring multiplexed display logic for rapid switching.}
                \resumeItem{Integrated LED indicators for class selection and weekly schedule display to enhance user experience.}
                \resumeItem{Demonstrated proficiency in digital system design and FPGA programming, showcasing practical application of hardware description languages.}
                \resumeItem{To view full details: \href{https://github.com/ferasaljoudi/ClassesSchedule}{\underline{ClassesSchedule}}}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Education}
        \resumeSubHeadingListStart
            \resumeSubheading
                {University of Regina, Degree}{Regina, SK}
                {Bachelor of Applied Science in Software Systems Engineering}{Sep. 2018 - Apr. 2025}
            \resumeSubHeadingListEnd
        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Reference}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Nick Dietrick}{C: 1 (306) 789-0591}
            {Manager for Construction Stations, SaskPower}{ndietrick@saskpower.com}
        \resumeSubheading
            {Puneet Kaur}{C: 1 (639) 560-3413}
            {Co-Manager, Urban Planet}{deolpuneetkaur@gmail.com}
    \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}